From the function-sheaf dictionary to quasicharacters of $p$-adic tori

### 2015-07-18 dictionary.tex
Minor edits before going to bed.

\begin{corollary}
For $\cs{E}\in \QCS(\pi_0(T))$, $\cs{F}\in {\QCS(T)}$ and $\cs{F}^0\in {\QCS(T^0)}$, there are canonical isomorphisms
\[
\Aut_{\QCS(\pi_0(T))}(\cs{E})\iso (\check{T}_\ell)^{\Weil{K}},
\quad
\Aut_{\QCS(T)}(\cs{F})\iso (\check{T}_\ell)^{\Weil{K}},
\quad
\Aut_{\QCS(T^0)}(\cs{F}^0)\iso 1.
\]
\end{corollary}

\begin{proof}
We already know $\Aut_{\QCS(T^0)}(\cs{E}) =1$ from Proposition~\ref{prop:connected}, part \ref{x3}.
By Theorem~\ref{thm:CSXK}, $\Aut(\cs{F})  \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx)$, canonically, for $X = T$ and $X=\pi_0(T)$ (and for $X= T^0$, though that case has already been treated by a different argument, above).
By \cite{bitan:discriminant}*{Eq 3.1} again, 
\[
\Hom((\pi_0(T)_{\bFq})_{\Weil{}},\EEx) \iso
\Hom(X_*(T_K)_{\Weil{K}},\EEx),
\]
canonically.
But $\Hom(X_*(T_K)_{\Weil{K}},\EEx) \iso \Hom(X_*(T_K),\EEx)^{\Weil{K}}$, canonically.
So, for any quasicharacter sheaf $\cs{F}$ for $T$,
\[
\Aut_\QCS{T}(\cs{F}) \iso (\check{T}_\ell)^{\Weil{K}},
\]
canonically, where $\check{T}_\ell$ is the $\ell$-adic dual torus $\Hom(X_*(T_K),\EEx)$.
The case $X= \pi_0(T)$ is treated recovers the same automorphism group since $\pi_0(\pi_0(T))_{\bFq} = \pi_0(T)_{\bFq}$.
\end{proof}

@@

Combining Corollary~\ref{cor:CS_tori} with Lemma~\ref{lem:LLCT} now produces the following commutative diagram of exact sequences:
\begin{equation}\label{eq:GLCT}
  \begin{tikzcd}[row sep=20, column sep=18]
{}  & 0 \arrow{d} & 0 \arrow{d} &  & \\ 
   & \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}}  \arrow{d} & \arrow{d} \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}} & 0 \arrow{d} & \\
    0 \rar & \QCSiso{\pi_0(T)} \arrow{r}{\pi_0^*} \arrow{d}
    & \QCSiso{T} \arrow{r}{\iota_0^*}  \arrow{d} & \QCSiso{T^0} \arrow{r} \arrow{d} & 0\\
   0 \arrow{r}  
 & \Hh^1(\Weil{}, \check{T}_\ell^{\mathcal{I}_K}) \arrow{r}{\text{infl'n}} \arrow{d}
 & \Hh^1(\Weil{K}, \check{T}_\ell) \arrow{r}{\text{rest'n}} \arrow{d}
 & \Hh^1(\mathcal{I}_K, \check{T}_\ell)^{\Weil{}} \arrow{r} \arrow{d}  
 & 0\\
 &  0  & 0 & 0 & 
  \end{tikzcd}
 \end{equation}
It is natural to ask if the vertical surjections can be defined directly, without making use of local class field theory.  
Even the case $T_K = \Gm{K}$ is remarkable, in which case \eqref{eq:GLCT} becomes

@@

As in \cite{Yu:09a}, the general case can be built up from the case $T_K = \Gm{K}$.

>>>>

\begin{corollary}
Let $T_K$ be an algebraic toris over $K$ and let $T$ be a Neron model for $T_K$.
For $\cs{E}\in \QCS(\pi_0(T))$, $\cs{F}\in {\QCS(T)}$ and $\cs{F}^0\in {\QCS(T^0)}$, there are canonical isomorphisms
\[
\Aut_{\QCS(\pi_0(T))}(\cs{E})\iso (\check{T}_\ell)^{\Weil{K}},
\quad
\Aut_{\QCS(T)}(\cs{F})\iso (\check{T}_\ell)^{\Weil{K}},
\quad
\Aut_{\QCS(T^0)}(\cs{F}^0)\iso 1,
\]
 where $\check{T}_\ell \ceq \Hom(X_*(T_K),\EEx)$, the $\ell$-adic dual torus to $T_K$.
\end{corollary}

\begin{proof}
We already know $\Aut_{\QCS(T^0)}(\cs{E}) =1$ from Proposition~\ref{prop:connected}, part \ref{x3}.
By Theorem~\ref{thm:CSXK}, $\Aut(\cs{F})  \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx)$, canonically, for $X = T$ and $X=\pi_0(T)$ (and for $X= T^0$, though that case has already been treated by a different argument, above).
By \cite{bitan:discriminant}*{Eq 3.1} again, 
\[
\Hom((\pi_0(T)_{\bFq})_{\Weil{}},\EEx) \iso
\Hom(X_*(T_K)_{\Weil{K}},\EEx),
\]
canonically.
But $\Hom(X_*(T_K)_{\Weil{K}},\EEx) \iso \Hom(X_*(T_K),\EEx)^{\Weil{K}}$, canonically.
So, for any quasicharacter sheaf $\cs{F}$ for $T$,
\[
\Aut_{\QCS(T)}(\cs{F}) \iso (\check{T}_\ell)^{\Weil{K}},
\]
canonically.
The case $X= \pi_0(T)$ recovers the same automorphism group since $\pi_0(\pi_0(T))_{\bFq} = \pi_0(T)_{\bFq}$.
\end{proof}

@@

Combining Corollary~\ref{cor:CS_tori} with Lemma~\ref{lem:LLCT} now produces the following commutative diagram of exact sequences:
\begin{equation}\label{eq:GLCT}
  \begin{tikzcd}[row sep=20, column sep=15]
{}  & 0 \arrow{d} & 0 \arrow{d} &  & \\ 
   & \Hh^0(\Weil{}, \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx))  \arrow{d} & \arrow{d} \Hh^0(\Weil{}, \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)) & 0 \arrow{d} & \\
    0 \rar & \QCSiso{\pi_0(T)} \arrow{r}{\pi_0^*} \arrow{d}
    & \QCSiso{T} \arrow{r}{\iota_0^*}  \arrow{d} & \QCSiso{T^0} \arrow{r} \arrow{d} & 0\\
   0 \arrow{r}  
 & \Hh^1(\Weil{}, \Hh^0(\mathcal{I}_K, \check{T}_\ell)) \arrow{r}{\text{infl'n}} \arrow{d}
 & \Hh^1(\Weil{K}, \check{T}_\ell) \arrow{r}{\text{rest'n}} \arrow{d}
 & \Hh^0(\Weil{}, \Hh^1(\mathcal{I}_K, \check{T}_\ell)) \arrow{r} \arrow{d}  
 & 0\\
 &  0  & 0 & 0 & 
  \end{tikzcd}
 \end{equation}
It is natural to ask if the vertical surjections can be defined directly, without making use of local class field theory.  
Even the case $T_K = \Gm{K}$ is remarkable, in which case \eqref{eq:GLCT} becomes

@@

As in \cite{yu:09a}, the general case can be built up from the case $T_K = \Gm{K}$.
